\large{Vipassana for Hackers} \\ \Huge{The Proposal} \\ \large\textit{Version 0.1}

### 2019-11-30 the-proposal/the-proposal.tex
proposal: wrangling the build to work with bibtex, updating the makefile

Research into the effects of meditation has been conducted in earnest for half a
century but the quality of research in this field varies wildly. Randomized
controlled trials were missing from much research conducted during the first few
decades of meditation study. The importance of active controls was often missed even
when randomized controlled trials were attempted. Double-blind studies are inherently
impossible with meditation research; a subject will always know if she is receiving
meditation instruction or an active control instruction. \cite{alteredtraits}

Add to these difficulties the very nature of meditation research itself. There are
many techniques of meditation and it is very important to capture the specific
technique under study to make meaningful assertions about its
effects. \cite{alteredtraits} However, even within the definition of a single
meditation technique there exist variations in instruction between
teachers and each student's comprehension of the instructions
received. \cite{davidson2015} Even if researchers could cement (or at least
accurately record) semantics and terminology, the subject of study is often unclear:
Are we looking for health benefits? Increases in productivity? Increases in
intelligence? How long these effects persist? How much do we want to explore concrete
hypotheses versus exploratory analysis of long-term effects? How much can be learned
about the nature of consciousness? Can these learnings be measured objectively or
even communicated meaningfully?

@@

Third is the exploratory research intended to objectively define
consciousness. As such research must pertain to all forms of consciousness it
therefore includes all non-human forms of consciousness. Findings will inform our
understanding of the Mind-Body Problem of psychology and philosophy, the entire field
of bioethics, and --- perhaps most importantly --- the nascent field of Artificial
Consciousness as a subfield of Artificial Intelligence. As of this writing, this
overarching integral field of study has yet to emerge and has no name as a discipline.

@@

\subsection{Participants}
- people & roles

@@

\begin{thebibliography}{99}

\bibitem{alteredtraits}
  Goleman D., Davidson R.J.
  \textit{Altered Traits.}
  ISBN: 9780399184390. September 2018.

\bibitem{davidson2015}
  Davidson R.J., Kaszniak A.W.
  \textit{Conceptual and methodological issues in research on mindfulness and meditation.}
  American Psychologist, Volume 70(7), Pages 581-92. October 2015.
  \url{https://doi.org/10.1037/a0039512}

\bibitem{entropicrevisited}
  Carhart-Harris, Robin L.
  \textit{The entropic brain - revisited}
  NEUROPHARMACOLOGY, Vol: 142, Pages: 167-178, ISSN: 0028-3908, 2018.

\end{thebibliography}

% \appendix*
% \input{sections/appendix1.tex}

>>>>

Research into the effects of meditation has been conducted in earnest for half a
century but the quality of research in this field varies wildly. Randomized
controlled trials were missing from much research conducted during the first few
decades of meditation study. The importance of active controls was often missed even
when randomized controlled trials were attempted. Double-blind studies are inherently
impossible with meditation research; a subject will always know if she is receiving
meditation instruction or an active control instruction. \cite{goleman2017altered}

Add to these difficulties the very nature of meditation research itself. There are
many techniques of meditation and it is very important to capture the specific
technique under study to make meaningful assertions about its
effects. \cite{goleman2017altered} However, even within the definition of a single
meditation technique there exist variations in instruction between
teachers and each student's comprehension of the instructions
received. \cite{davidson2015conceptual} Even if researchers could cement (or at least
accurately record) semantics and terminology, the subject of study is often unclear:
Are we looking for health benefits? Increases in productivity? Increases in
intelligence? How long these effects persist? How much do we want to explore concrete
hypotheses versus exploratory analysis of long-term effects? How much can be learned
about the nature of consciousness? Can these learnings be measured objectively or
even communicated meaningfully?

@@

Third is the exploratory research intended to objectively define
consciousness. As such research must pertain to all forms of consciousness it
therefore includes all non-human forms of consciousness. Findings will inform our
understanding of the Mind-Body Problem of psychology and philosophy, the entire field
of bioethics, and --- perhaps most importantly --- the nascent field of Artificial
Consciousness as a subfield of Artificial Intelligence. \cite{hildt2019artificial} As of this
writing, this overarching integral field of study has yet to emerge and has no name
as a discipline.

@@

\subsection{Participants}
- people and roles

@@

\bibliography{the-proposal}{}
\bibliographystyle{chicago}

%\begin{thebibliography}{99}
%
%\bibitem{alteredtraits}
%  Goleman D., Davidson R.J.
%  \textit{Altered Traits.}
%  ISBN: 9780399184390. September 2018.
%
%\bibitem{davidson2015}
%  Davidson R.J., Kaszniak A.W.
%  \textit{Conceptual and methodological issues in research on mindfulness and meditation.}
%  American Psychologist, Volume 70(7), Pages 581-92. October 2015.
%  \url{https://doi.org/10.1037/a0039512}
%
%\bibitem{hildt2019}
%  Artificial Intelligence: Does Consciousness Matter?
%  \todo{stop doing this and use bibtex}
%
%\bibitem{entropicrevisited}
%  Carhart-Harris, Robin L.
%  \textit{The entropic brain - revisited}
%  NEUROPHARMACOLOGY, Vol: 142, Pages: 167-178, ISSN: 0028-3908, 2018.
%
%
%\end{thebibliography}
%
% \appendix*
% \input{sections/appendix1.tex}
